### 2014-06-28 patchy-selection-paper.tex

@@

>>>>

\subsection{PETER'S VERSION}

@@

\subsection{GRAHAM'S VERSION}

We have developed a simple set of approximations to describe the rate
at which organisms in a patchy environment adapt through novel
mutations or migration from other nearby patches (eqn.
\eqref{eqn:mutrate} and \eqref{eqn:migrate}), and the relative
probability of each of these outcomes (eqn. \eqref{eqn:parallel_prob}). 
We have also determined the characteristic genomic length scales over which
the various signals of hitchhiking should be visable
(eqn. \eqref{eqn:haplotype_length} and ).

These results show that the probability of parallel adaptation is
independent of both the population density and the beneficial
selection coefficient. This follows from the fact that these
parameters both increase the rate of adaptation via both migration and
mutation equally. Thus they are important for the time-scale over
which adaptation occurs but not the mode of adaptation. This
constrasts with models of convergent adaptation within panmictic
populations \citep{} and geographically spread populations adapting to
homogeneous populations \citep{RalphCoop}, where the number of
adaptive alleles increases with the population size/density. In all of these models the dependence on the beneficial selection
coefficient is absent or weak, due to the fact that selection both
aids establiishment of new alleles and the spread of existing
alleles.

The primary determinant of the probability of parallel adaptation is
$\sigma/\sqrt{s_d}$, the characteristic geographic distance of the
allele frequency decay off the patch. We find that patches that are close together on
this scale will adapt via migration, but there will be a sharp
transition to convergent adaptation as we move to patches that are further apart.

In coming to this conclusion, we have ignored the possibility of very long distance migration,
instead focusing local dispersal (as parameterized by a Gaussian
dispersal model). However, dispersal distributions can be very heavy
tailed, with a small fraction of individuals moving very long distances indeed, in
addition over long time-scales very rare chance events (mice sucked up in
hurricanes etc) could play a role in spreading migrant alleles. Such
tail events could greatly increase the probability of parallel
adaptation above that predicted by our model. Furthermore, if
adaptive alleles do move between distant patches via rare long distance
migration they will be associated with a much longer shared haplotype than
predicted by eqn. \eqref{eqn:haplotype_length}. As such we view our
results as a null model by which the contribution of long distribution
migrants to adaptation could be empirically judged.

We have also assumed that the alleles have a fitness effect in
heterozygotes both on and off the patch. However, 
 recessive alleles could also contribute to adaptation to patchy
 environments. \gc{should we cite Nachman eg here}.  Our
 simple branching process framework does not easily accomodate recessive
 alleles as it ignores the selection interaction of alleles, and so a
 different approach will be needed. At first sight it
 seems like recessive alleles may be able to contribute to adaptation
 via migration over longer distances, as the migrant alleles will be at low
 frequency between patches and so usually invisible to
 selection. However, this fact also means that they are unlikely to
 establish on the beneficial patch upon reaching it via migration. As
 such it is not clear what our intuition should be about the
 contribution of recessive alleles to adaptation via migration.

\gc{will write a couple more broader paragraphs}

The falling cost of sequencing over the next decade offers the
opportunity to investigate the genomics of parallel adaptation over a
large s
Over the coming decade population genomic data will be generated

\plr{Note that optimal $s_m$ for migration makes migration harder to spot.}
